%% start of file `moderncv_ntrp_template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
%
% Modded by ntrp (nitropowered@gmail.com)
% Modded by PritvhviRaj Narendra

\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[green]{classic}                % idem

\usepackage[T1]{fontenc}
% character encoding
\usepackage[utf8x]{inputenc}                  

%\usepackage{tgpagella}
%\renewcommand{\sfdefault}{\rmdefault}

\definecolor{lightgreen}{rgb}{0.7,1,0.7}

\usepackage{eso-pic}



\usepackage[savepos]{zref}% http://ctan.org/pkg/zref
\makeatletter
\@ifundefined{zsaveposx}{\let\zsaveposx\zsavepos}{}
\newcounter{hposcnt}
\renewcommand*{\thehposcnt}{hpos\number\value{hposcnt}}
\newcommand*{\tab}[2]{% \tab{<len>}{<stuff>}
	\stepcounter{hposcnt}%
	\zsaveposx{\thehposcnt}%
	\zref@refused{\thehposcnt}%
	\kern\dimexpr-\zposx{\thehposcnt}sp+1in+\oddsidemargin\relax%
	\rlap{\kern#1\relax#2}%
	\kern\dimexpr-1in-\oddsidemargin+\zposx{\thehposcnt}sp\relax%
}

% adjust the page margins
\usepackage[scale=0.86]{geometry}
\recomputelengths                             
% required when changes are made to page layout lengths

\fancyfoot{} % clear all footer fields

\fancyfoot[RE,LO]{\footnotesize } % other info in "inner" position of footer line

\renewcommand*{\quotestyle}[1]{{\quotefont\textcolor{color0}{#1}}}
\renewcommand*{\titlestyle}[1]{{\titlefont\textcolor{color2}{#1}}}

\renewcommand*{\recomputecvlengths}{%
	\setlength{\quotewidth}{0.93\textwidth}
}	

% personal data
\firstname{PrithviRaj}
\familyname{Narendra}

\address{Bengaluru, India}{}    % optional, remove the line if not wanted
\mobile{+91-9886535655}                    % optional, remove the line if not wanted
%\phone{<Phone number>}                      % optional, remove the line if not wanted
%\fax{<Fax number>}                          % optional, remove the line if not wanted
\email{prithvi@appiko.org}                      % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[84pt]{placeholder.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
\quote{I'm a co-founder of Appiko, an early stage start-up whose mission is to develop technology for wildlife conservation. I care about sustainability and conservation of the environment. I am proficient with embedded systems and lean iterative development cycle of designing, prototyping and testing for mass manufacturing electronic devices.}% \textbf{TODO based on application}}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


\newcommand{\leftRatingIndent}{48ex}
\newcommand{\rightRatingIndent}{105ex}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

%Section

\section{\textbf{Experience}}
\subsection{Working}

\cventry{Oct 2017 -- present}{Co-founder}{\href{https://appiko.org/}{Appiko}}{Bengaluru}{}{As a founder I've to keep track of Appiko's big picture while managing of the day to day firefighting activities. I've lead and taken part in the development and manufacturing of long-range animal warning systems and low-power low-cost app-controlled camera trapping equipment. }

\cventry{Aug 2015 -- Jan 2017}{Embedded Engineer}{\href{http://lofelt.com/}{Lofelt}}{Berlin}{}{Firmware \& factory test routine development during the entire product development lifecycle of Basslet.}

\cventry{Nov 2014 -- Apr 2015}{Firmware Engineer}{\href{http://bluvision.com/}{BluVision}}{Berlin}{}{Firmware and Android app development engineer for Bluetooth beacons. } % arguments 3 to 6 are optional

\cventry{Oct 2011 - Jul 2012}{Research Assistant}{\href{http://www.dese.iisc.ernet.in/}{DESE}, Indian Institute of Science}{Bengaluru}{}{Being the project assistant of Dr. André Pittet I was involved in the complete product design cycle of fabricating gadgets such as camera traps and animal collars for wildlife researchers.} % arguments 3 to 6 are optional

\subsection{Projects}
\cventry{Jan 2014 -- Sep 2014}{Master Thesis}{ \href{https://www.sics.se/groups/networked-embedded-systems-group-nes}{Swedish Institute of Computer Science}}{Stockholm}{}{Comparison of BLE and 802.15.4's data rate, latency, reliability and energy consumption.} % arguments 3 to 6 are optional

\cventry{Feb 2009 -- June 2011}{Team Member/Leader}{\href{https://www.isro.gov.in/Spacecraft/studsat-1}{Project STUDSAT-1/2}}{Bengaluru}{}{In STUDSAT-1, India's first student pico-satellite, I developed the electronics and software for the camera payload and lead the entire 25+ people team in the STUDSAT-2 for a year.} % arguments 3 to 6 are optional

\subsection{Publications}
\cventry{Oct 2015}{\href{http://www.simonduquennoy.net/papers/narendra15ble.pdf}{BLE \& IEEE 802.15.4 in the IoT: Evaluation \& Interoperability Considerations}}{Proceedings of the International Conference on Interoperability in IoT (EAI InterIoT 2015)}{}{}{} % arguments 3 to 6 are optional


%Section
\section{\textbf{Education}}
\cventry{Sep 2012 -- Sep 2014}{\href{http://www.masterschool.eitictlabs.eu/}{Masters in EIT Digital Master School}}{}{\newline Major in \emph{\href{http://www.masterschool.eitictlabs.eu/programmes/es/}{Embedded Systems}}, Minor in \emph{\href{http://www.masterschool.eitictlabs.eu/programmes/minor/}{Innovation and Entrepreneurship}}}{}{Year 1: \emph{\href{http://tue.nl/}{Technische Universiteit Eindhoven}}, Eindhoven; Year 2: \emph{\href{https://www.kth.se/en}{Royal Institute of Technology}}, Stockholm} % arguments 3 to 6 are optional

\cventry{Sep 2007 -- May 2011}{Bachelors in Electronics and Communication}{\href{http://rvce.edu.in/}{RV College of Engineering}}{Bengaluru}{}{Best Outgoing Student Award from the Electronics \& Communication Dept. for the 2007-11 batch.} % arguments 3 to 6 are optional

%Section
\section{\textbf{Additional Experience/Volunteer}}
\cventry{Mar 2017 -- Aug 2017}{Driving Force}{\href{embeddedforher.com}{Embedded for Her program}}{}{}{Embedded for Her is a skill development program in the field of embedded systems for women to increase gender diversity in this domain. I lead this program full-time with volunteers from \href{fsmk.org}{FSMK}. }

%Section
\section{\textbf{Further Info}}
%\cvline{Birth}{\small 20/09/1989 \normalsize}
%\cvline{Elance}{\small \url{<Link to profile>}\normalsize}
\cvcomputer{LinkedIn}{\small \url{linkedin.com/in/prithvirajnarendra}\normalsize}{Github}{\small \url{github.com/EarthLord}\normalsize}
%\cvline{Blog}{\small \url{<Link to profile>}\normalsize}
%\cvline{Skype}{\small <skype>\normalsize}

\end{document}